Preregistered as Code: Gender differences in Machiavellianism

### 2021-08-09 preregistration.Rmd
add discussion to preregistration

We created this document to illustrate Preregistration as Code.
We therefore do not discuss the results.

>>>>

This document only serves to illustrate Preregistration as Code.
We, therefore, do not discuss the results.
After we have acquired the data, we realized that we had to change the code for reading the data (see commit [6556a93](https://github.com/aaronpeikert/repro-tutorial/commit/6556a9395fcdd600b5b0c5358f92a2c6635ae360)).
We do not believe that these changes influence the results substantively.
